---
title: "Variables aléatoires"
subtitle: "BoostR"
author: "Vincent Guillemot"
date: "Lundi 15 sept. 2014"
output: ioslides_presentation
runtime: shiny
---

# L'aléatoire

## L'aléatoire

> Définition

## Exemples

Déterministe | Aléatoire
--- | ---
Âge | Âge

## Probabilité

Diagramme de Venn

## Probabilité -- Densité


## Probabilité -- Distribution



## Types de mesures

- Mesure qualitative
     + nominale
     + ordinale
- Mesure quantitative
     + discrète
     + continue

--|--------------------------------|---
A | Catégorie socio-professionelle | ...
B | Un peu, beaucoup, ...          | ...
C | Age (années)                   | ...
D | Distance (?)                   | ...

# Lois discrètes usuelles

## Bernoulli

## Binomiale

## Poisson

# Lois continues usuelles

## Uniforme

```{r source_unif, echo=FALSE}
source('~/unif.R')
source('~/gaussienne.R')
source('~/chideux.R')
source('~/student.R')
```

```{r unif, echo = FALSE}
unif()
```

## Gaussienne

```{r gaussienne, echo = FALSE}
gaussienne()
```

## $\chi^2$

```{r chideux, echo = FALSE}
chideux()
```

## Fisher

## Student

```{r student, echo = FALSE}
student()
```

# Parentées




